```{r data, echo = FALSE}
inpD <-"L:/promec/Elite/LARS/2018/november/Rolf final/txt/"
data <- read.delim(paste0(inpD,"proteinGroups.txt"),row.names=1,sep="\t",header = T)
summary(data)
decoyPrefix="REV"
contaminantPrefix="CON"
hdr="LFQ.intensity."
```


```{r dataNorm, echo = FALSE}
dataNorm=log2(data[,grep(hdr, names(data))])
#set.seed(1)
#dataNorm[dataNorm==-Inf]<-rnorm(1,mean=mean(dataNorm[dataNorm!=-Inf]),sd=sd(dataNorm[dataNorm!=-Inf]))
#dataNorm[dataNorm==-Inf]=NA
summary(dataNorm)
```

```{r VennDetail}
#https://bioconductor.org/packages/release/bioc/vignettes/VennDetail/inst/doc/VennDetail.html
#install.packages('BiocManager')
head(dataNorm$LFQ.intensity.15+dataNorm$LFQ.intensity.12)
BiocManager::install("VennDetail")
library(VennDetail)
ven <- venndetail(list(Red = dataNorm$LFQ.intensity.19+dataNorm$LFQ.intensity.26+dataNorm$LFQ.intensity.29, White = dataNorm$LFQ.intensity.15+dataNorm$LFQ.intensity.12+dataNorm$LFQ.intensity.30))
ven <- venndetail(dataNorm)
plot(ven)
plot(ven, type = "vennpie")
```

```{r write-output, echo = FALSE}
write.table(dataNorm,file=paste0(inpD,"log2data.txt"), sep = "\t")
#dump(dataNorm,file=paste0(inpD,"dataNorm.R"))
```


```{r impute, echo = FALSE}
#install.packages('mice')
library(mice)
#install.packages('randomForest')
library(randomForest)
dataNormImp=mice(dataNorm, method="rf")
dataNormImpCom <- complete(dataNormImp,1)
row.names(dataNormImpCom)<-row.names(dataNorm)
summary(dataNormImpCom)
```

```{r write-output, echo = FALSE}
write.csv(dataNormImpCom,file=paste0(inpD,"log2dataImp.csv"))
#write.csv(factors,file=paste0(inpD,"dataNormImpComFactor.csv"))
dataNormImpCom <- read.csv(paste0(inpD,"log2dataImp.csv"),row.names=1,header = T)
#factors<-read.csv(paste0(inpD,"dataNormImpComFactor.csv"))
#dump(dataNorm,file=paste0(inpD,"dataNorm.R"))
```

```{r PCA, echo = FALSE}
plot(princomp(dataNormImpCom))
biplot(prcomp(as.matrix(t(dataNormImpCom)),scale = T))
biplot(prcomp(dataNormImpCom,scale = F))
biplot(prcomp(dataNormImpCom,scale = T),col=c(1,8), cex=c(0.5, 0.4))
```


```{r DEqMS}
#https://rdrr.io/bioc/DEqMS/f/vignettes/DEqMS-package-vignette.Rmd
#install.packages("BiocManager")
#BiocManager::install("DEqMS")
library(DEqMS)
#df.prot = read.table("F:\\promec\\Animesh\\Yan_miR_Protein_table.flatprottable.txt",stringsAsFactors = FALSE,header = TRUE, quote = "", comment.char = "",sep = "\t")
# filter at 1% protein FDR and extract TMT quantifications
dat.log=dataNormImpCom
boxplot(dat.log,las=2,main="")
cond = as.factor(c("w","w","r","r","r","w"))
# The function model.matrix is used to generate the design matrix
design = model.matrix(~0+cond) # 0 means no intercept for the linear model
colnames(design) = gsub("cond","",colnames(design))
# you can define one or multiple contrasts here
x <- c("r-w")
contrast =  makeContrasts(contrasts=x,levels=design)
fit1 <- lmFit(dat.log, design)
fit2 <- contrasts.fit(fit1,contrasts = contrast)
fit3 <- eBayes(fit2)
# assign a extra variable `count` to fit3 object, telling how many PSMs are 
# quantifed for each protein
df.prot=data
library(matrixStats)
count_columns = "MS.MS.count."
#psm.count.table = data.frame(count = rowMins(as.matrix(df.prot[,grep(count_columns, names(df.prot))])))+1
rownames(fit3$coefficients)
fit3$count = rowMins(as.matrix(df.prot[,grep(count_columns, names(df.prot))]))+1
fit4 = spectraCounteBayes(fit3)
# n=30 limits the boxplot to show only proteins quantified by <= 30 PSMs.
VarianceBoxplot(fit4,n=30,main=inpD,xlab="PSM count")
VarianceScatterplot(fit4,main=inpD)
DEqMS.results = outputResult(fit4,coef_col = 1)
#if you are not sure which coef_col refers to the specific contrast,type
head(fit4$coefficients)
# a quick look on the DEqMS results table
head(DEqMS.results)
# Save it into a tabular text file
write.table(DEqMS.results,paste0(inpD,hdr,"DEqMS.results.txt"),sep = "\t",row.names = F,quote=F)
#install.packages("ggrepel")
library(ggrepel)
# Use ggplot2 allows more flexibility in plotting
DEqMS.results$log.sca.pval = -log10(DEqMS.results$sca.P.Value)
ggplot(DEqMS.results, aes(x = logFC, y =log.sca.pval )) + 
    geom_point(size=0.5 )+
    theme_bw(base_size = 16) + # change theme
    xlab(expression("log2(red/white)")) + # x-axis label
    ylab(expression(" -log10(P-value)")) + # y-axis label
    geom_vline(xintercept = c(-1,1), colour = "red") + # Add fold change cutoffs
    geom_hline(yintercept = 3, colour = "red") + # Add significance cutoffs
    geom_vline(xintercept = 0, colour = "black") + # Add 0 lines
    scale_colour_gradient(low = "black", high = "black", guide = FALSE)+
    geom_text_repel(data=subset(DEqMS.results, abs(logFC)>1&log.sca.pval > 3),
                    aes( logFC, log.sca.pval ,label=gene)) # add gene label

fit4$p.value = fit4$sca.p
# volcanoplot highlight top 20 proteins ranked by p-value here
volcanoplot(fit4,coef=1, style = "p-value", highlight = 20,names=rownames(fit4$coefficients))


df.LFQ<-dataNormImpCom
boxplot(df.LFQ)
library(matrixStats)
#psm.count.table = data.frame(count = rowMins(as.matrix(df.prot[,grep(count_columns, names(df.prot))])))+1

pep.count.table = data.frame(count = rowMins(as.matrix(data[,112:217])))
# Minimum peptide count of some proteins can be 0
# add pseudocount 1 to all proteins
pep.count.table$count = pep.count.table$count+1
protein.matrix = as.matrix(df.LFQ)
fit1 = lmFit(protein.matrix,design = design)
fit2 = contrasts.fit(fit1,contrasts = contrast)
fit3 <- eBayes(fit2)

count_columns = "Peptides."
rownames(fit3$coefficients)

fit3$count = rowMins(as.matrix(data[,grep(count_columns, names(data))]))+1
min(fit3$count)

fit4 = spectraCounteBayes(fit3)
VarianceBoxplot(fit4, n=20, main = hdr,xlab="peptide count + 1")
#class = as.factor(c("H","H","H","L","L","L"))
#design = model.matrix(~0+class) # fitting without intercept

DEqMS.results = outputResult(fit4,coef_col = 1)
# Add Gene names to the data frame
rownames(df.prot) = df.prot$Majority.protein.IDs
DEqMS.results$Gene.name = df.prot[DEqMS.results$gene,]$Gene.names
head(DEqMS.results)
write.table(DEqMS.results,paste0(inpD,hdr,"R-W.DEqMS.results.txt"),sep = "\t",row.names = F,quote=F)
#dat.gene.nm = medianSweeping(dat.psm.log,group_col = 2)
head(DEqMS.results)
VarianceBoxplot(fit4,n=20)
peptideProfilePlot(dat=df.prot)#,col=2,gene="TGFBR2")
VarianceScatterplot(fit4, xlab="log2(LFQ)")
limma.prior = fit4$s2.prior
abline(h = log(limma.prior),col="green",lwd=3 )
legend("topright",legend=c("DEqMS prior variance","Limma prior variance"),
        col=c("red","green"),lwd=3)
op <- par(mfrow=c(1,2), mar=c(4,4,4,1), oma=c(0.5,0.5,0.5,0))
Residualplot(fit4,  xlab="log2(PSM count)",main="DEqMS")
x = fit3$count
y = log(limma.prior) - log(fit3$sigma^2)
plot(log2(x),y,ylim=c(-6,2),ylab="Variance(estimated-observed)", pch=20, cex=0.5,
     xlab = "log2(PSMcount)",main="Limma")
#install.packages("LSD")
library(LSD)
op <- par(mfrow=c(1,2), mar=c(4,4,4,1), oma=c(0.5,0.5,0.5,0))
x = fit3$count
y = fit3$s2.post
heatscatter(log2(x),log(y),pch=20, xlab = "log2(PSMcount)", 
     ylab="log(Variance)",
     main="Posterior Variance in Limma")

y = fit4$sca.postvar
heatscatter(log2(x),log(y),pch=20, xlab = "log2(PSMcount)",
     ylab="log(Variance)", 
     main="Posterior Variance in DEqMS")

```


```{r ROTS, echo = FALSE}
#iocManager::install("ROTS")#, version = "3.8")
dataNormImpCom[is.na(dataNormImpCom)]=5
summary(dataNormImpCom)
factors<-c(rep(0,3), rep(1,3))
library(ROTS)
results = ROTS(data = dataNormImpCom, groups = factors , B = 1000 , K = 500 , seed = 1234)
write.csv(summary(results, fdr = 1),file=paste0(inpD,hdr,"rots.csv"))
names(results) 
summary(results, fdr = 0.2)
plot(results, fdr = 0.5, type = "volcano")
#P61203-2;P61203
#plot(results, fdr = 0.5, type = "heatmap")
```



```{r MSstats, echo = FALSE}
#https://bioconductor.org/packages/3.3/bioc/vignettes/MSstats/inst/doc/MSstats-manual.pdf
library('MSstats')
QuantData<-dataProcess(SRMRawData)
head(QuantData$ProcessedData)
## based on multiple comparisons (T1 vs T3; T1 vs T7; T1 vs T9)
comparison1<-matrix(c(-1,0,1,0,0,0,0,0,0,0),nrow=1)
comparison2<-matrix(c(-1,0,0,0,0,0,1,0,0,0),nrow=1)
comparison3<-matrix(c(-1,0,0,0,0,0,0,0,1,0),nrow=1)
comparison<-rbind(comparison1,comparison2, comparison3)
row.names(comparison)<-c("T3-T1","T7-T1","T9-T1")
testResultMultiComparisons<-groupComparison(contrast.matrix=comparison,data=QuantData)
## Calculate sample size for future experiments:
#(1) Minimal number of biological replicates per condition
designSampleSize(data=testResultMultiComparisons$fittedmodel,numSample=TRUE,
desiredFC=c(1.25,1.75),FDR=0.05,power=0.8)
#(2) Power calculation
designSampleSize(data=testResultMultiComparisons$fittedmodel,numSample=2,
desiredFC=c(1.25,1.75),FDR=0.05,power=TRUE)```
```

```{r SAM, echo = FALSE}
#https://github.com/MikeJSeo/SAM
install.packages(c("samr", "matrixStats", "GSA", "shiny", "shinyFiles", "openxlsx"))
source("http://bioconductor.org/biocLite.R")
biocLite("impute")
library(shiny)
library(shinyFiles)
runGitHub("SAM", "MikeJSeo")
```




```{r NA}
#impute(data, method = "mixed",randna = fData(naset)$randna,mar = "knn", mnar = "min")
md.pattern(datasel)
dataimp <- mice(datasel,m=length(colnames(datasel))/2,maxit=length(colnames(datasel)),meth='pmm',seed=1)
dataimp <- complete(dataimp,length(colnames(datasel))/2)
heatmap(as.matrix(dataimp),col=colscl)
```

```{r Scale}
datascale=t(scale(t(dataimp))) # takes away the polynomial in YFP data
heatmap(as.matrix(datascale),col=colscl)
```

```{r DistCor}
dataasmat<-data.matrix(datascale)
cor(data)
dissimilarityc <- 1 - cor(dataasmat,method = "s")
distancec <- as.dist(dissimilarityc)
col.clus <- hclust(distancec, "aver")
dissimilarityr <- 1 - cor(t(dataasmat),method = "s")
distancer <- as.dist(dissimilarityr)
row.clus <- hclust(distancer, "aver")
heatmap(as.matrix(datascale),col=colscl)
cr <- rainbow(nrow(dataasmat))
cc <- rainbow(ncol(dataasmat))
heatmap((na.omit(dataasmat)), RowSideColors = cr, ColSideColors = cc,Rowv = as.dendrogram(row.clus), Colv = as.dendrogram(col.clus),cexRow=1.5,cexCol=1.5 )
```


```{r Quantile}
dataasmat<-normalize.quantiles(dataasmat)
rn<-rownames(dataasmat)
cn<-colnames(dataasmat)
colnames(dataasmat)<-cn
rownames(dataasmat)<-rn
```

```{r AdjPval}
p.adjust(10^(-data$X.log10P),method = c("hochberg"), n = length(data$X.log10P))
p.adjust(data$pv,method = c("hochberg"), n = length(data$pv))
```

```{r interpolate}
data<-read.table("c:/Users/animeshs/Downloads/Sunshine hours.txt",sep='\t',header=T)
summary(data$SONNENSCHEINDAUER)
dp=approx(data$SONNENSCHEINDAUER)
summary(dp)
plot(dp$SONNENSCHEINDAUER,data$SONNENSCHEINDAUER)
install.packages('zoo')
library('zoo')
dp<-rollmean(data,1)
dp<-na.approx(data)
summary(dp)
write.table(dp,"c:/Users/animeshs/Downloads/SunshineDP.txt",sep='\t')
```



```{r lmfit}
source("https://bioconductor.org/biocLite.R")
biocLite("golubEsets")
library(golubEsets)
data()
data(golubTrain)
golubTrain
golub<-data.frame(golubTrain@exprs)
labelgb <- factor(c(rep("ALL",27),rep("AML",11)))
names(golub) <- labelgb
golub2<-log2(golub)
plot(golub2)
biocLite('limma')
library('limma')
fit3 = lmFit(golub2)
e3 = eBayes(fit3)
tab3<-topTable(e3, number=nrow(golub))
head(tab3)
fit3@.Data[[9]]
fit4 = lmFit(golub2, design)
```


```{r shuffle}
ecoli <- read.delim("Y:/felles/PROTEOMICS and XRAY/Ani/Christina/Strainssamples.txt", header=TRUE, na.strings='', sep="\t")
for  (cnt in 1:6){
  cnt
}
  ecoli_shuffle <- ecoli_shuffle[sample(nrow(ecoli)),]
write.csv(file="Y:/felles/PROTEOMICS and XRAY/Ani/Christina/Strainssamples_shuffled_rn.csv",x=ecoli_shuffle,row.names = F)
```


```{r prot}
install.packages("PTXQC")
library("PTXQC")
help(package = "PTXQC")
vignette("PTXQC-InputData", package = "PTXQC")
txt_folder = "F:/promec/Elite/LARS/2016/desember/Lymphoma/Results"
r = createReport(txt_folder)
cat(paste0("\nReport generated as '", r$report_file, "'\n\n"))

```


```{r Cluster}
colscl <- colorRampPalette(c("darkblue", "chocolate"), space = "rgb")(100)
heatmap(na.omit(as.matrix(data)),col=colscl)
```




```{r SVA}
#https://academic.oup.com/bioinformatics/article-lookup/doi/10.1093/bioinformatics/btu375
#source("http://www.bioconductor.org/biocLite.R")
#biocLite(c("Biobase","sva","bladderbatch","snpStats"))
  library(sva)
  library(devtools)
  library(Biobase)
  library(bladderbatch)
  library(snpStats)

data(bladderdata)
pheno = pData(bladderEset)
edata = exprs(bladderEset)

mod = model.matrix(~as.factor(cancer) + as.factor(batch),data=pheno)
fit = lm.fit(mod,t(edata))
hist(fit$coefficients[2,],col=2,breaks=100)
table(pheno$cancer,pheno$batch)

batch = pheno$batch
modcombat = model.matrix(~1, data=pheno)
modcancer = model.matrix(~cancer, data=pheno)
combat_edata = ComBat(dat=edata, batch=batch, mod=modcombat, par.prior=TRUE, prior.plots=FALSE)

combat_fit = lm.fit(modcancer,t(combat_edata))
hist(combat_fit$coefficients[2,],col=2,breaks=100)

plot(fit$coefficients[2,],combat_fit$coefficients[2,],col=2,
      xlab="Linear Model",ylab="Combat",xlim=c(-5,5),ylim=c(-5,5))
abline(c(0,1),col=1,lwd=3)

mod = model.matrix(~cancer,data=pheno)
mod0 = model.matrix(~1, data=pheno)
sva1 = sva(edata,mod,mod0,n.sv=2)

summary(lm(sva1$sv ~ pheno$batch))

boxplot(sva1$sv[,2] ~ pheno$batch)
points(sva1$sv[,2] ~ jitter(as.numeric(pheno$batch)),col=as.numeric(pheno$batch))

modsv = cbind(mod,sva1$sv)
fitsv = lm.fit(modsv,t(edata))

par(mfrow=c(1,2))
plot(fitsv$coefficients[2,],combat_fit$coefficients[2,],col=2,
      xlab="SVA",ylab="Combat",xlim=c(-5,5),ylim=c(-5,5))
abline(c(0,1),col=1,lwd=3)
plot(fitsv$coefficients[2,], fit$coefficients[2,],col=2,
      xlab="SVA",ylab="linear model",xlim=c(-5,5),ylim=c(-5,5))
abline(c(0,1),col=1,lwd=3)

data(for.exercise)
controls <- rownames(subject.support)[subject.support$cc==0]
use <- seq(1, ncol(snps.10), 10)
ctl.10 <- snps.10[controls,use]

xxmat <- xxt(ctl.10, correct.for.missing=FALSE)
evv <- eigen(xxmat, symmetric=TRUE)
pcs <- evv$vectors[,1:5]

pop <- subject.support[controls,"stratum"]
plot(pcs[,1],pcs[,2],col=as.numeric(pop),
      xlab="PC1",ylab="PC2")
legend(0,0.15,legend=levels(pop),pch=19,col=1:2)
```

---
title: "batch-effect-analysis"
author: "Ani"
date: "Monday, Feb 15, 2016"
output: html_document
---

