```{r data, echo = FALSE}
setwd("L:/promec/Animesh/Lisa/")
inpD <-paste0(getwd())
inpF<-paste0(inpD,"/Heatmap Ani.xlsx")
data <- readxl::read_xlsx(inpF)
```

```{r sel-data-cols, echo = FALSE}
#install.packages("scales")
dataSel<-data[40:74,3:7]
cN<-paste0(data[39,3:7],colnames(dataSel))
rN<-paste0(t(data[40:74,2]),rownames(dataSel))
dataSel<-sapply(dataSel,as.numeric)
colnames(dataSel)<-cN
rownames(dataSel)<-rN
summary(dataSel)
hist(as.matrix(dataSel))
min(dataSel,na.rm=T)
max(dataSel,na.rm=T)
write.csv(cbind(rownames(dataSel),dataSel),paste0(inpF,".parse.R.csv"),row.names = F)
dataSel=scales::squish(as.matrix(dataSel),c(-1,1))
summary(dataSel)
hist(as.matrix(dataSel))
#install.packages('pheatmap')
svgPHC<-pheatmap::pheatmap(dataSel,fontsize_row=6,cluster_rows=FALSE,cluster_cols=FALSE)
ggplot2::ggsave(file=paste0(inpF,"clusterPlot.metabolomics.row.scaled.m1p1.svg"),plot=svgPHC)#,  ```
#https://www.biostars.org/p/192253/#192284
bk1 <- c(seq(-1,-0.01,by=0.01))
bk2 <- c(seq(0.01,1,by=0.01))
breaksList <- c(bk1,bk2)
palette<-colorRampPalette(rev(RColorBrewer::brewer.pal(n = 7, name = "RdYlBu")))(length(breaksList))
svgPHC<-pheatmap::pheatmap(dataSel,fontsize_row=6,color=palette,cluster_rows=FALSE,cluster_cols=FALSE,breaks = breaksList)
#install.packages("svglite")
#install.packages("ggplot2")
ggplot2::ggsave(file=paste0(inpF,"clusterPlot.metabolomics.row.scaled.m1p1.breaks.svg"),plot=svgPHC)#,  ```
```
