---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
#https://cran.r-project.org/web/packages/tidyquant/vignettes/TQ04-charting-with-tidyquant.html
install.packages("tidyquant")
library("tidyquant")
``````


```{r cars}
c("YAR.OL", "GOOG", "TEL.OL") %>%
YAR<-tq_get(x='YAR.OL',get = "stock.prices", from = "2016-01-01", to = "2017-01-01")
    tq_get(get = "stock.prices", from = "2016-01-01", to = "2017-01-01")
YAR  %>%
ggplot(aes(x = date, y = close, open = open,
               high = high, low = low, close = close)) +
    geom_candlestick() +
    geom_bbands(ma_fun = SMA, sd = 2, n = 20) +
    labs(title = "AAPL Candlestick Chart", 
         subtitle = "BBands with SMA Applied", 
         y = "Closing Price", x = "") + 
    coord_x_date(xlim = c(end - weeks(24), end),
                 ylim = c(100, 120)) + 
    theme_tq()
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
