```{r TEiMeta, echo = FALSE}
#AEC: automated execution context / data provenance and its manifest - Salmon guy
#https://bioconductor.org/packages/release/bioc/vignettes/tximeta/inst/doc/tximeta.html
BiocManager::install("tximeta")
```

```{r VRS.ga4gh, echo = FALSE}
#https://github.com/ga4gh/vrs
BiocManager::install(c("MSnbase", "protViz"))
```

```{r seqCol, echo = FALSE}
#https://github.com/yafeng/SpectrumAI
BiocManager::install(c("MSnbase", "protViz"))
```


```{r SpectrumAI, echo = FALSE}
#https://github.com/yafeng/SpectrumAI
BiocManager::install(c("MSnbase", "protViz"))
```

```{r pkgs, echo = FALSE}
#https://cran.r-project.org/web/packages/diceR/vignettes/overview.html
install.packages("diceR")
library(glmnet)
```

```{r setup, echo = FALSE}
inpD <-"F:/mgf/"
inpF<-"20150512_BSA_The-PEG-envelope.raw.profile.MGF"#paste0(inpD,"20150512_BSA_The-PEG-envelope.raw.profile.MGF")
setwd(inpD)  #set your working directory
mzml_path = inpD # set file path to which raw files are located
infile_name = inpF  # PSM table file name
outfile_name = paste0(inpF,".out")  #set corresponding output file name
Frag.ions.tolerance= 0.02 # 0.02 Da tolerance for MS2 fragment ions mass accuracy.
relative=FALSE  # set TRUE if ppm value is used for Frag.ions.tolerance```
```


```{r script}
#https://github.com/yafeng/SpectrumAI/blob/master/SpectrumAI.R
#!/usr/bin/env Rscript
library(protViz)
library(MSnbase)
library(stringr)
#The df.psm dataframe should have at least the following columns with exactly same names (the order can be different): "SpectraFile", "ScanNum", "Peptide",  "sub_pos" 
df.psm=read.table(infile_name,sep="\t",header=T,comment.char = "",quote = "")
df.output = InspectSpectrum(df.psm)
write.table(df.output,outfile_name,sep="\t",quote=F,row.names=F)

df.sub = df.output[df.output$status == "checked",]
saav_psm_passed = df.sub[df.sub$flanking_ions_support=="YES",]$PrecursorError.ppm.
saav_psm_failed = df.sub[df.sub$flanking_ions_support=="NO",]$PrecursorError.ppm.

pdf("precursorError.histogram.plot.pdf",width = 10, height = 7)
par(mfrow=c(1,2))
hist(saav_psm_passed,breaks=20,xlab="precMassError (ppm)",main="SpectrumAI curated")
hist(saav_psm_failed,breaks=20,xlab="precMassError (ppm)",main="SpectrumAI discarded")
```
